Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli

### 2023-12-29 manuscript_draft.tex
finalizing typos and nsim

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli},
  pdfauthor={Erin M. Buchanan1, Mahmoud M. Elsherif2, Jason Geller3, Chris L. Aberson4, Necdet Gurkan5, Ettore Ambrosini6,26, Tom Heyman7, Maria Montefinese8, Wolf Vanpaemel9, Krystian Barzykowski10, Carlota Batres11, Katharina Fellnhofer12, Guanxiong Huang13, Joseph McFall14,27, Gianni Ribeiro15, Jan P. Röer16, José L. Ulloa17, Timo B. Roettger18, K. D. Valentine19,28, Antonino Visalli20, Kathleen Schmidt21, Martin R. Vasilev22, Giada Viviani23, Jacob F. Miranda24, \& Savannah C. Lewis25},
  pdflang={en-EN},
  pdfkeywords={accuracy in parameter estimation, power, sampling, simulation, hypothesis testing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli}
\author{Erin M. Buchanan\textsuperscript{1}, Mahmoud M. Elsherif\textsuperscript{2}, Jason Geller\textsuperscript{3}, Chris L. Aberson\textsuperscript{4}, Necdet Gurkan\textsuperscript{5}, Ettore Ambrosini\textsuperscript{6,26}, Tom Heyman\textsuperscript{7}, Maria Montefinese\textsuperscript{8}, Wolf Vanpaemel\textsuperscript{9}, Krystian Barzykowski\textsuperscript{10}, Carlota Batres\textsuperscript{11}, Katharina Fellnhofer\textsuperscript{12}, Guanxiong Huang\textsuperscript{13}, Joseph McFall\textsuperscript{14,27}, Gianni Ribeiro\textsuperscript{15}, Jan P. Röer\textsuperscript{16}, José L. Ulloa\textsuperscript{17}, Timo B. Roettger\textsuperscript{18}, K. D. Valentine\textsuperscript{19,28}, Antonino Visalli\textsuperscript{20}, Kathleen Schmidt\textsuperscript{21}, Martin R. Vasilev\textsuperscript{22}, Giada Viviani\textsuperscript{23}, Jacob F. Miranda\textsuperscript{24}, \& Savannah C. Lewis\textsuperscript{25}}
\date{}

@@

The authors made the following contributions. Erin M. Buchanan: Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Resources, Software, Validation, Visualization, Writing - original draft, Writing - review \& editing; Mahmoud M. Elsherif: Data curation, Resources, Writing - original draft, Writing - review \& editing; Jason Geller: Data curation, Resources, Writing - original draft, Writing - review \& editing; Chris L. Aberson: Data curation, Writing - original draft, Writing - review \& editing; Necdet Gurkan: Data curation, Writing - review \& editing; Ettore Ambrosini: Resources, Writing - original draft, Writing - review \& editing; Tom Heyman: Resources, Writing - original draft, Writing - review \& editing; Maria Montefinese: Resources, Writing - original draft, Writing - review \& editing; Wolf Vanpaemel: Resources, Writing - original draft, Writing - review \& editing; Krystian Barzykowski: Data curation, Resources, Writing - original draft, Writing - review \& editing; Carlota Batres: Resources, Writing - review \& editing; Katharina Fellnhofer: Resources, Writing - original draft, Writing - review \& editing; Guanxiong Huang: Resources, Writing - original draft, Writing - review \& editing; Joseph McFall: Resources, Writing - review \& editing; Gianni Ribeiro: Resources, Writing - original draft, Writing - review \& editing; Jan P. Röer: Resources, Writing - original draft, Writing - review \& editing; José L. Ulloa: Resources, Writing - original draft, Writing - review \& editing; Timo B. Roettger: Visualization, Formal analysis, Writing - original draft, Writing - review \& editing; K. D. Valentine: Conceptualization, Writing - original draft, Writing - review \& editing; Antonino Visalli: Writing - original draft, Writing - review \& editing; Kathleen Schmidt: Writing - original draft, Writing - review \& editing; Martin R. Vasilev: Writing - original draft, Writing - review \& editing; Giada Viviani: Writing - original draft, Writing - review \& editing; Jacob F. Miranda: Project administration, Writing - original draft, Writing - review \& editing; Savannah C. Lewis: Project administration, Writing - original draft, Writing - review \& editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Harrisburg University of Science and Technology\\\textsuperscript{2} University of Leicester, Department of Vision Sciences\\\textsuperscript{3} Department of Psychology, Princeton University\\\textsuperscript{4} Illumin Analytics\\\textsuperscript{5} Stevens Institute of Technology\\\textsuperscript{6} Department of Neuroscience, University of Padova, Padova, Italy\\\textsuperscript{7} Methodology and Statistics Unit, Institute of Psychology, Leiden University\\\textsuperscript{8} Department of Developmental and Social Psychology, University of Padova, Italy\\\textsuperscript{9} University of Leuven\\\textsuperscript{10} Applied Memory Research Laboratory, Institute of Psychology, Jagiellonian University\\\textsuperscript{11} Franklin and Marshall College\\\textsuperscript{12} ETH Zürich\\\textsuperscript{13} Department of Media and Communication, City University of Hong Kong\\\textsuperscript{14} Department of Psychology, University of Rochester\\\textsuperscript{15} School of Psychology, The University of Queensland\\\textsuperscript{16} Department of Psychology and Psychotherapy, Witten/Herdecke University\\\textsuperscript{17} Programa de Investigación Asociativa (PIA) en Ciencias Cognitivas, Centro de Investigación en Ciencias Cognitivas (CICC), Facultad de Psicología, Universidad de Talca\\\textsuperscript{18} University of Oslo\\\textsuperscript{19} Massachusetts General Hospital\\\textsuperscript{20} IRCCS San Camillo Hospital (Venice Lido, Italy)\\\textsuperscript{21} Ashland University\\\textsuperscript{22} Bournemouth University\\\textsuperscript{23} University of Padova\\\textsuperscript{24} California State University East Bay\\\textsuperscript{25} University of Alabama, Tuscaloosa\\\textsuperscript{26} Padova Neuroscience Center, University of Padova, Padova, Italy\\\textsuperscript{27} Children's Institute, Inc\\\textsuperscript{28} Harvard Medical School}

>>>>

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli},
  pdfauthor={Erin M. Buchanan1, Mahmoud M. Elsherif2, Jason Geller3, Chris L. Aberson4, Necdet Gurkan5, Yangyang Yu5, Ettore Ambrosini6,27, Tom Heyman7, Maria Montefinese8, Wolf Vanpaemel9, Krystian Barzykowski10, Carlota Batres11, Katharina Fellnhofer12, Guanxiong Huang13, Bastian Jaeger14, Joseph McFall15,28, Gianni Ribeiro16, Jan P. Röer17, Jordan Suchow5, José L. Ulloa18, Timo B. Roettger19, K. D. Valentine20,29, Antonino Visalli21, Kathleen Schmidt22, Martin R. Vasilev23, Giada Viviani24, Jacob F. Miranda25, \& Savannah C. Lewis26},
  pdflang={en-EN},
  pdfkeywords={accuracy in parameter estimation, power, sampling, simulation, hypothesis testing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli}
\author{Erin M. Buchanan\textsuperscript{1}, Mahmoud M. Elsherif\textsuperscript{2}, Jason Geller\textsuperscript{3}, Chris L. Aberson\textsuperscript{4}, Necdet Gurkan\textsuperscript{5}, Yangyang Yu\textsuperscript{5}, Ettore Ambrosini\textsuperscript{6,27}, Tom Heyman\textsuperscript{7}, Maria Montefinese\textsuperscript{8}, Wolf Vanpaemel\textsuperscript{9}, Krystian Barzykowski\textsuperscript{10}, Carlota Batres\textsuperscript{11}, Katharina Fellnhofer\textsuperscript{12}, Guanxiong Huang\textsuperscript{13}, Bastian Jaeger\textsuperscript{14}, Joseph McFall\textsuperscript{15,28}, Gianni Ribeiro\textsuperscript{16}, Jan P. Röer\textsuperscript{17}, Jordan Suchow\textsuperscript{5}, José L. Ulloa\textsuperscript{18}, Timo B. Roettger\textsuperscript{19}, K. D. Valentine\textsuperscript{20,29}, Antonino Visalli\textsuperscript{21}, Kathleen Schmidt\textsuperscript{22}, Martin R. Vasilev\textsuperscript{23}, Giada Viviani\textsuperscript{24}, Jacob F. Miranda\textsuperscript{25}, \& Savannah C. Lewis\textsuperscript{26}}
\date{}

@@

The authors made the following contributions. Erin M. Buchanan: Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Resources, Software, Validation, Visualization, Writing - original draft, Writing - review \& editing; Mahmoud M. Elsherif: Data curation, Resources, Writing - original draft, Writing - review \& editing; Jason Geller: Data curation, Resources, Writing - original draft, Writing - review \& editing; Chris L. Aberson: Data curation, Writing - original draft, Writing - review \& editing; Necdet Gurkan: Data curation, Writing - review \& editing; Yangyang Yu: Data curation, Writing - review \& editing; Ettore Ambrosini: Resources, Writing - original draft, Writing - review \& editing; Tom Heyman: Resources, Writing - original draft, Writing - review \& editing; Maria Montefinese: Resources, Writing - original draft, Writing - review \& editing; Wolf Vanpaemel: Resources, Writing - original draft, Writing - review \& editing; Krystian Barzykowski: Data curation, Resources, Writing - original draft, Writing - review \& editing; Carlota Batres: Resources, Writing - review \& editing; Katharina Fellnhofer: Resources, Writing - original draft, Writing - review \& editing; Guanxiong Huang: Resources, Writing - original draft, Writing - review \& editing; Bastian Jaeger: Resources, Writing - review \& editing; Joseph McFall: Resources, Writing - review \& editing; Gianni Ribeiro: Resources, Writing - original draft, Writing - review \& editing; Jan P. Röer: Resources, Writing - original draft, Writing - review \& editing; Jordan Suchow: Resources, Writing - review \& editing; José L. Ulloa: Resources, Writing - original draft, Writing - review \& editing; Timo B. Roettger: Formal analysis, Visualization, Writing - original draft, Writing - review \& editing; K. D. Valentine: Conceptualization, Writing - original draft, Writing - review \& editing; Antonino Visalli: Writing - original draft, Writing - review \& editing; Kathleen Schmidt: Writing - original draft, Writing - review \& editing; Martin R. Vasilev: Writing - original draft, Writing - review \& editing; Giada Viviani: Writing - original draft, Writing - review \& editing; Jacob F. Miranda: Project administration, Writing - original draft, Writing - review \& editing; Savannah C. Lewis: Project administration, Writing - original draft, Writing - review \& editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Analytics, Harrisburg University of Science and Technology\\\textsuperscript{2} Department of Vision Sciences, University of Leicester\\\textsuperscript{3} Department of Psychology, Princeton University\\\textsuperscript{4} Illumin Analytics\\\textsuperscript{5} Stevens Institute of Technology\\\textsuperscript{6} Department of Neuroscience, University of Padova\\\textsuperscript{7} Methodology and Statistics Unit, Institute of Psychology, Leiden University\\\textsuperscript{8} Department of Developmental and Social Psychology, University of Padova\\\textsuperscript{9} University of Leuven\\\textsuperscript{10} Applied Memory Research Laboratory, Institute of Psychology, Jagiellonian University\\\textsuperscript{11} Franklin and Marshall College\\\textsuperscript{12} ETH Zürich\\\textsuperscript{13} Department of Media and Communication, City University of Hong Kong\\\textsuperscript{14} Tilburg University\\\textsuperscript{15} Department of Psychology, University of Rochester\\\textsuperscript{16} School of Psychology, The University of Queensland\\\textsuperscript{17} Department of Psychology and Psychotherapy, Witten/Herdecke University\\\textsuperscript{18} Programa de Investigación Asociativa (PIA) en Ciencias Cognitivas, Centro de Investigación en Ciencias Cognitivas (CICC), Facultad de Psicología, Universidad de Talca\\\textsuperscript{19} University of Oslo\\\textsuperscript{20} Massachusetts General Hospital\\\textsuperscript{21} IRCCS San Camillo Hospital\\\textsuperscript{22} Ashland University\\\textsuperscript{23} Bournemouth University\\\textsuperscript{24} University of Padova\\\textsuperscript{25} California State University East Bay\\\textsuperscript{26} University of Alabama\\\textsuperscript{27} Padova Neuroscience Center, University of Padova\\\textsuperscript{28} Children's Institute Inc.\\\textsuperscript{29} Harvard Medical School}
